---
title: "MIS 381N SCO Project 1"
author: "GROUP 3: Drew LIEBERMAN, Kartik SHARMA, Yuwen WANG, Vicky ZHANG"
date: "February 8, 2016"
output: html_document
---

```{r, echo=FALSE}
setwd("C:/Users/Yuwen Wang/Desktop/SCO Project1")
library(lpSolveAPI)
```

# Problem 1

Let `x1`,`x2`,`x3`,`x4`,`x5`,`x6`,`x7`,`x8`,`x9`,`x10` represent the initial investment in each of the ten bonds. The objective is to minimize the initial cost and matching the liability cash flows for the coming 8 years.

$min \ 102x_1 + 99x_2 + 101x_3 + 98x_4 + 98x_5 + 104x_6 + 100x_7 + 101x_8 + 102x_9 + 94x_{10}$

$s.t.$

$Year\ 1:\ (100+5)x_1 + 3.5x_2 + 5x_3 + 3.5x_4 + 4x_5 + 9x_6 + 6x_7 + 8x_8 + 9x_9 + 7x_{10}\ =\ 12,000$

$Year\ 2:\ (100+3.5)x_2 + (100+5)x_3 + 3.5x_4 + 4x_5 + 9x_6 + 6x_7 + 8x_8 + 9x_9 + 7x_{10}\ =\ 18,000$

$Year\ 3:\ (100+3.5)x_4 + 4x_5 + 9x_6 + 6x_7 + 8x_8 + 9x_9 + 7x_{10}\ =\ 20,000$

$Year\ 4:\ (100+4)x_5 + 9x_6 + 6x_7 + 8x_8 + 9x_9 + 7x_{10}\ =\ 20,000$

$Year\ 5:\ (100+9)x_6 + (100+6)x_7 + 8x_8 + 9x_9 + 7x_{10}\ =\ 16,000$

$Year\ 6:\ (100+8)x_8 + 9x_9 + 7x_{10}\ =\ 15,000$

$Year\ 7:\ (100+9)x_9 + 7x_{10}\ =\ 12,000$

$Year\ 8:\ (100+7)x_{10}\ =\ 10,000$

# Problem 2
```{r}
library(lpSolveAPI)

my.lp <- make.lp(8,10) # 8 Constraints, 10 decision variables
print (my.lp)

Colnames=c('x1','x2','x3','x4','x5','x6','x7','x8','x9','x10')
Rownames=c('Y1','Y2','Y3','Y4','Y5','Y6','Y7','Y8')
dimnames(my.lp)<-list(Rownames,Colnames)

add.constraint(my.lp,c(105,3.5,5,3.5,4,9,6,8,9,7), "=",12000)  #Y1
add.constraint(my.lp,c(0,103.5,105,3.5,4,9,6,8,9,7), "=",18000) #Y2
add.constraint(my.lp,c(0,0,0,103.5,4,9,6,8,9,7), "=",20000) #Y3
add.constraint(my.lp,c(0,0,0,0,104,9,6,8,9,7), "=",20000) #Y4
add.constraint(my.lp,c(0,0,0,0,0,109,106,8,9,7), "=",16000) #Y5
add.constraint(my.lp,c(0,0,0,0,0,0,0,108,9,7), "=",15000) #Y6
add.constraint(my.lp,c(0,0,0,0,0,0,0,0,109,7), "=",12000) #Y7
add.constraint(my.lp,c(0,0,0,0,0,0,0,0,0,107), "=",10000) #Y8

set.objfn(my.lp, c(102,99,101,98,98,104,100,101,102,94))
lp.control(my.lp,sense='min')

write.lp(my.lp,'Project1.lp',type='lp')
solve(my.lp)
print (get.objective(my.lp))
print (get.variables(my.lp))

```

# Problem 3
```{r,echo=FALSE}
# Define the function
dedicate_g3 <- function(P,C,M,L)
{
  Mat <- matrix(0,length(L),length(P))
  for (j in 1:length(P))
  {
    Maturity = M[j]
    if (Maturity > 1) {
      #print(Maturity)
      Mat[1:Maturity - 1,j] <- C[j]
    }
    Mat[Maturity,j] <- 100 + C[j]
    if (sum(Maturity + 1) < nrow(Mat))
    {
      Mat[sum(Maturity + 1):nrow(Mat),j] = 0
    }
  }
  Mat[1,length(P)] = -1
  Mat[2,length(P)] = 1
  for (Col in length(P):ncol(Mat))
  {
    for (Row in 2:nrow(Mat))
    {
      if (Mat[Row,sum(Col - 1)] == 1)
      {
        Mat[Row,Col] = -1
      }
      if (Mat[sum(Row - 1),Col] == -1)
      {
        Mat[Row,Col] = 1
      }
    }
  }
  
  
  Proj <- make.lp(length(L),ncol(Mat))
  for (i in 1:ncol(Mat))
  {
    set.column(Proj,i,Mat[,i])
  }
  Price <- matrix(0,length(P))
  for (i in 1:length(P))
  {
    Price[i] = P[i]
  }
  set.objfn(Proj,Price)
  set.constr.type(Proj,rep("=",nrow(Mat)))
  set.rhs(Proj,L)
  lp.control(Proj,sense = 'min')
  sol = solve(Proj)
  dual = get.sensitivity.rhs(Proj)
  #print(dual)
  
  returns = c(Proj, dual)
  return (returns)
  #Will return the whole thing so you can then type get.variables(object) and other actions like that
  #return(get.variables(Proj))
}
```

Testing of our function `dedicate_g3(P,C,M,L)`:

```{r}
P = c(102,99,101,98,98,104,100,101,102,94)
C = c(5,3.5,5,3.5,4,9,6,8,9,7)
M = c(1,2,2,3,4,5,5,6,7,8)
L = c(12000,18000,20000,20000,16000,15000,12000,10000)

Portfolio<-dedicate_g3(P,C,M,L)

print (get.objective(Portfolio[[1]]))
print (get.variables(Portfolio[[1]]))
```

# Problem 4

Get US Treasury Bonds quotes from `http://www.wsj.com/mdc/public/page/2_3020-treasury.html` 

\* **STARTING DATE**: pulled on **Feb 8, 2016**, which should be treated as the STARTING DATE.

\* **MATURITY DATES**: chosen to match the date of liability stream. For some of the maturity dates there are multiple bonds available, we just randomly pick one bond for each maturity date.

\* **PRICES**: calculated the average of bid and ask price ($price\ =\ (bid\ +\ ask)\ /\ 2$) as the price of a bond, which is a widely used approach in academics.

```{r}
raw_quotes = read.csv("US Treasury Bonds.csv")
print (raw_quotes)

P4 = (raw_quotes$Bid + raw_quotes$Asked) / 2
C4 = raw_quotes$Coupon
M4 = c(1,1,1,
       2,2,2,
       3,3,3,
       4,4,4,
       5,5,
       6,6,
       7,7,
       8,8,
       9,9,
       10,10,
       11,
       12)
L4 = c(9,9,10,10,6,6,9,9,10,10,5,3) * 1000000

Portfolio_4<-dedicate_g3(P4,C4,M4,L4)

print (get.objective(Portfolio_4[[1]]))
print (get.variables(Portfolio_4[[1]]))

```

```{r,echo=FALSE}
print (Portfolio_4$duals)
plot(Portfolio_4$duals[1:12],
     xlab = 'Maturity dates', xaxt = 'n',
     ylab = 'Change in initial investment ($)',
     pch = 19, cex = 1.5)
axis(1, labels = unique(raw_quotes$Maturity), 
     at = seq(from = 1, by = 1, length.out = length(L4)))
title("Sensitivity of $1 Change in Liability")
```

The first 12 duals correspond to the 12 constraints we have, and the rest 26 correspond to the non-negative constraints. 

The first 12 duals can be interpreted as follows: if liability in period i is reduced by $1, the intial investment in period 0 will reduce by $dual amount$. For example, for the first dual, if liability in year 1 reduces by $1, our initial payout would reduce by $0.97.  
